%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% the .tex file. The resume.cls file provides the resume style used for
% structuring document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

% Document margins
\usepackage[left=0.75in,top=0.75in,right=0.75in,bottom=0.75in]{geometry}

% Your name, address, phone number, and email
\name{Mario E. Muscarella}
\address{Department of Plant Biology, University of Illinois at Urbana-Champaign}
\address{Phone: (517) 285-8391; E-mail: mmuscar@illinois.edu}

\begin{document}
\thispagestyle{empty}

%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------

\begin{rSection}{Education}

  {\bf Indiana University} \hfill {\em Aug 2012 -- Jun 2016} \\
  Biology, Ph.D.; Evolution, Ecology \& Behavior Program

  {\bf Michigan State University} \hfill {\em June 2010 -- Aug 2012} \\
  Microbiology \& Molecular Genetics \\
  Ecology and Evolutionary Biology

  {\bf Armstrong State University} \hfill {\em Aug 2004 -- May 2008} \\
  Biology, Summa Cum Laude, B.S.

\end{rSection}

%-------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%-------------------------------------------------------------------------------

\begin{rSection}{Experience}

  %--Appointment------------------------------------------------------------------
    \begin{rSubsection}{Postdoctoral Research Associate}
      {August 2016 -- Present}{University of Illinois}{Urbana, IL}
      \item O'Dwyer Lab: Theoretical Ecology, Microbial Ecology, Traits Based Ecology, Phylogenetic Patterns
    \end{rSubsection}

%--Appointment------------------------------------------------------------------
  \begin{rSubsection}{Graduate Research Assistant}
    {June 2010 -- July 2016}{Indiana University}{Bloomington, IN}
    \item Lennon Lab: Aquatic Microbiology, Molecular and Ecological Strategies
                      of Resource Utilization; \\
                      Interactions between Microbes and Molecules
  \end{rSubsection}

%--Appointment------------------------------------------------------------------
  \begin{rSubsection}{Associate Instructor}{January 2013 -- May 2015}
    {Indiana University}{Bloomington, IN}
    \item Courses Taught: Quantitative Biodiversity; Environmental Microbiology;
                          Introductory Biology Lab
  \end{rSubsection}

%--Appointment------------------------------------------------------------------
  \begin{rSubsection}{Graduate Teaching Assistant}{June 2011 -- August 2012}
    {Michigan State University}{East Lansing, MI}
    \item Courses Taught: Microbial Metagenomics; Cells and Molecules Lab;
                          Introductory Microbiology Lab
  \end{rSubsection}

%--Appointment------------------------------------------------------------------
  \begin{rSubsection}{Research Technician}{June 2008 -- June 2010}
    {University of Georgia Marine Institute}{Sapelo Island, GA}
    \item Booth Lab: Georgia Coastal Ecosystems LTER, \& Sapelo Island Microbial
                     Observatory
  \end{rSubsection}

%--Appointment------------------------------------------------------------------
  %\begin{rSubsection}{Undergraduate Research Assistant}{Sep 2005 -- May 2008}
  %  {Armstrong State University}{Savannah, GA}
  %  \item Awong-Taylor Lab: Environmental Microbiology
  %\end{rSubsection}

%--Appointment------------------------------------------------------------------
  %\begin{rSubsection}{Labaratory Technician}{Sep 2005 -- May 2008}
  %  {Armstrong State University}{Savannah, GA}
  %  \item Introductory Microbiology Labs: Media and Reagent Preperation;
  %                                        Lab Oversight
  %\end{rSubsection}

\end{rSection}

%-------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%-------------------------------------------------------------------------------

\begin{rSection}{Publications}

%--Publication------------------------------------------------------------------
Long H, Sung W, Kucukyildirim S, Williams E, Miller S, Guo W, Patterson C, Gregory C, Strauss C, Stone C, Berne C, Kysela D, Shoemaker WR, {\bf Muscarella ME}, Luo H, Lennon JT, Brun YV, Lynch M (In Review) Evoltionary determinants of genome-wide nucleotide composition

%--Publication------------------------------------------------------------------
 Lennon JT, Placella SA, {\bf Muscarella ME} (2017) Relic DNA contributes minimally to estimates of microbial diversity. bioRxiv, DOI: https://doi.org/10.1101/131284

%--Publication------------------------------------------------------------------
Patrick T. Kelly, Tom Bell, Alexander, J. Reisinger, Trisha Spanbauer, Lauren Bortolotti, Jennifer Brentrup, Christian Briseno-Avena, Xiaoli Dong, Alison Flanagan, Elizabeth Follett, Julia Grosse, Tamar Guy-Haim, Meredith A. Holgerson, Rachel Hovel, Jessica Luo, Nicole Millette, Aric Mine, {\bf Mario E. Muscarella}, Sam Oliver, Heidi Smith (2017) Ecological Dissertations in the Aquatic Sciences (Eco-DAS): An effective networking and professional development opportunity for early career aquatic scientists. Limnology and Oceanography Bulletin, DOI: 10.1002/lob.10180

%--Publication------------------------------------------------------------------
Tamar Guy-Haim, Harriet Alexander, Tom W Bell, Raven L Bier, Lauren E
Bortolotti, Christian Briseño-Avena, Xiaoli Dong, Alison M Flanagan, Julia
Grosse, Lars Grossmann, Sarah Hasnain, Rachel Hovel, Cora A Johnston, Dan R
Miller, {\bf Mario Muscarella}, Akana E Noto, Alexander J Reisinger, Heidi J
Smith, Karen Stamieszkin (2017) What are the type, direction, and strength
of species, community, and ecosystem responses to warming in aquatic mesocosm
studies and their dependency on experimental characteristics? A systematic
review protocol. Environmental Evidence, 6(1):6

%--Publication------------------------------------------------------------------
{\bf Muscarella ME}, Jones SE, Lennon JT (2016) Species sorting along a
subsidy gradient alters bacterial community stability. Ecology, 97(8):2034-2043

%--Publication------------------------------------------------------------------
Shoemaker WR*, {\bf Muscarella ME}*, Lennon JT (2015). Genome Sequence of the
Soil Bacterium {\em Janthinobacterium} sp. KBS071. Genome Announcements,
3(3):e00689-15

%--Publication------------------------------------------------------------------
{\bf Muscarella ME}, Bird KC, Larsen ML, Placella SA, Lennon JT (2014).
Phosphorus resource heterogeneity affects the structure and function of
microbial food webs. Aquatic Microbial Ecology, 73(3):259-272

%--Publication------------------------------------------------------------------
Lennon JT, Hamilton SK, {\bf Muscarella ME}, AS Grandy, K Wickings, SE Jones
(2013). A source of terrestrial organic carbon to investigate the browning of
aquatic ecosystems. PLoS ONE 8(10):e75771

%--Publication------------------------------------------------------------------
J. Awong-Taylor, K. Craven, L. Griffiths, C. Bass and {\bf M. Muscarella} (2008)
. Comparison of biochemical and molecular methods for the identification of
bacterial isolates associated with failed loggerhead sea turtle eggs. Journal of
Applied Microbiology. 104:1244-1251

%--Publication------------------------------------------------------------------
Kathryn S. Craven, Judy Awong-Taylor, Laura Griffiths, Crystal Bass \&
{\bf Mario Muscarella} (2007). Identification of Bacterial Isolates from
Unhatched Loggerhead ({\em Caretta caretta}) Sea Turtle Eggs in Georgia, USA.
Marine Turtle Newsletter 115:9-11

%--Note-------------------------------------------------------------------------
{\em (* co-first authors)}

\end{rSection}

%-------------------------------------------------------------------------------
%	GRANTS SECTION
%-------------------------------------------------------------------------------

\begin{rSection}{Grants}

%--Grant------------------------------------------------------------------------
    \begin{rSubsection}{NSF Doctoral Dissertation Improvement Grant
      {\normalfont \em \$19,004}}{2015 -- 2017}{}{}
      \item DISSERTATION RESEARCH: Metabolic Resource Partitioning: Scaling
      Microbial Physiology from Individual Activity to Ecosystem Function
    \end{rSubsection}

%--Grant------------------------------------------------------------------------
    \begin{rSubsection}{Indiana Academy of Sciences Senior Research Grant
      {\normalfont \em \$2,200}}{2014 -- 2015}{}{}
      \item Metabolic Fate of Terrestrial Carbon Resources: Anabolic vs.
      Catabolic Processes
    \end{rSubsection}

%--Grant------------------------------------------------------------------------
    \begin{rSubsection}{Huron Mountain Wildlife Foundation Grant Renewal
      {\normalfont \em \$3,299}}{2012 -- 2014}{}{}
      \item Browning of Freshwater Ecosystems: Will Terrestrial Carbon Loading
      Alter the Diversity and Function of Aquatic Microbial Communities?
    \end{rSubsection}

%--Grant------------------------------------------------------------------------
    \begin{rSubsection}{Huron Mountain Wildlife Foundation
      {\normalfont \em \$5,600}}{2011 -- 2012}{}{}
      \item Browning of Freshwater Ecosystems: Will Terrestrial Carbon Loading
      Alter the Diversity and Function of Aquatic Microbial Communities?
    \end{rSubsection}

\end{rSection}

%-------------------------------------------------------------------------------
%	HONORS AND AWARDS SECTION
%-------------------------------------------------------------------------------

\begin{rSection}{Honors and Awards}

%--Award------------------------------------------------------------------------
    \begin{rSubsection}{Floyd Microbiology Summer Fellowship
      {\normalfont \em \$2000}}{2013 -- 2014}{}{}
      \item Department of Biology, Indiana University, Bloomington, IN
    \end{rSubsection}

%--Award------------------------------------------------------------------------
    \begin{rSubsection}{Floyd Microbiology Travel Award
      {\normalfont \em \$300}}{2012}{}{}
      \item Department of Biology, Indiana University, Bloomington, IN
    \end{rSubsection}

%--Award------------------------------------------------------------------------
    \begin{rSubsection}{University Distinguished Fellowship}{2010}{}{}
      \item Graduate School, Michigan State University, East Lansing, MI
    \end{rSubsection}

%--Award------------------------------------------------------------------------
    \begin{rSubsection}{Early Start Fellowship}{2010}{}{}
      \item College of Natural Sciences, Michigan State University, East
      Lansing, MI
    \end{rSubsection}

%--Award------------------------------------------------------------------------
    \begin{rSubsection}{Les Davenport Award}{2008}{}{}
      \item Biology Department, Armstrong State University. Savannah, GA
    \end{rSubsection}

%--Award------------------------------------------------------------------------
    \begin{rSubsection}{ASB Research Award in Microbiology}{2008}{}{}
      \item Presented at the 69th Annual Association of Southeastern Biologists
      Conference \\
      Best Paper Presentation in the Area of Microbiology
    \end{rSubsection}

%--Award------------------------------------------------------------------------
    \begin{rSubsection}{Faculty Recognition Award}{2007}{}{}
      \item Biology Department, Armstrong State University. Savannah, GA
    \end{rSubsection}

\end{rSection}

%-------------------------------------------------------------------------------
%	SYMPOSIA SECTION
%-------------------------------------------------------------------------------

\begin{rSection}{Symposia and Working Groups}

  \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
  2016 & Ramon Margalef Summer Colloquia \\
       & Microbes in a Changing World: Diversity and Biogeochemistry, Barcelona, Spain \\
  2016 & Predicting the Response of Host-associated Microbiomes to Disturbance \\  &  Santa Fe Institute Working Group, Santa Fe, NM \\
  2016 & Eco-DAS XII: Ecological Dissertations in the Aquatic Sciences, Honolulu, HI  \\
  \end{tabular}

\end{rSection}

%-------------------------------------------------------------------------------
%	WORKSHOPS SECTION
%-------------------------------------------------------------------------------

\begin{rSection}{Workshops}

  \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
  2013 & Software Carpentry Workshop, Bloomington IN \\
  2012 & DOM Fluorescence Workshop, INSTAAR, Boulder CO \\
  2010 & Mothur Software Workshop, Detroit MI \\
  \end{tabular}

\end{rSection}

%-------------------------------------------------------------------------------
%	PROFESSIONAL AFFILIATIONS SECTION
%-------------------------------------------------------------------------------

\begin{rSection}{Professional Affiliations}
  \begin{tabular}{ @{} >{\em}l @{\hspace{6ex}} l }
    Ecological Society of America &  \\
    Association for the Sciences of Limnology and Oceanography &  \\
    Great Lakes Ecological Observatory Network &  \\
    American Society for Microbiology & \\
  \end{tabular}

\end{rSection}


%-------------------------------------------------------------------------------
%	SERVICE SECTION
%-------------------------------------------------------------------------------

\begin{rSection}{Service}

%--Service----------------------------------------------------------------------
    \begin{rSubsection}{Reviewer}{}{}{}
        \item Journals: {\em Aquatic Ecology, Aquatic Microbial Ecology, Environmenatal Microbiology, Environmental Science \& Technology, ISME, L\&O Letters, Microbial Ecology}
        \item Books: {\em Processes in Microbial Ecology, Kirchman (2012)}
    \end{rSubsection}

%--Service----------------------------------------------------------------------
    \begin{rSubsection}{Committee Member}{}{}{}
        \item Michigan State University: {\em MMG Grad Committee}
        \item Indiana University: {\em IU Biology GRW Transportation}
    \end{rSubsection}

%--Service----------------------------------------------------------------------
    \begin{rSubsection}{Outreach}{}{}{}
        \item Jim Holland Summer Enrichement Program (Indiana University):
        {\em Stream Health \& Micro-Invertebrate Assessment} (2012 -- 2016)
        \item Wonderlab Science Museum (Bloomington, IN): {\em Good Microbes
        Exhibit} (2012 -- 2014)
        \item Women in STM (Indiana University): {\em Stream Micro-Invertebrate
        Assessment} (2012)
    \end{rSubsection}

%--Service----------------------------------------------------------------------
    \begin{rSubsection}{Professional Society Leadership}{}{}{}
        \item Graduate Student Liaison for Microbial Ecology Section, ESA
              (2013 -- 2015)
        \item
        \item
    \end{rSubsection}

%--Service----------------------------------------------------------------------
    \begin{rSubsection}{Special Session Co-Organizer}{}{}{}
        \item The Dance Between Microbes and Molecules
				\item ASLO Summer Meeting, Santa Fe NM (2016)
    \end{rSubsection}

%--Service----------------------------------------------------------------------
    \begin{rSubsection}{Conference Co-Organizer}{}{}{}
        \item 2015 Midwest Ecology and Evolution Conference.
				Bloomington, IN
    \end{rSubsection}

%--Service----------------------------------------------------------------------
    \begin{rSubsection}{Course Development}{}{}{}
        \item Quantitative Biodiversity (2015, Indiana University)
        \item \hspace{2ex} repo: https://github.com/quantitativebiodiversity
        \item \hspace{2ex} website:
        http://documentup.com/QuantitativeBiodiversity/QuantitativeBiodiversity
    \end{rSubsection}

\end{rSection}

%-------------------------------------------------------------------------------
%	INVITED SEMINARS
%-------------------------------------------------------------------------------

\begin{rSection}{Invited Seminars}

%--Presentation-----------------------------------------------------------------
  {\bf Muscarella ME} (2015) Microbes and resources: individuals, communities,
	and ecosystem function. Program in Ecology, Evolution, and Conservation
	Biology, University of Illinois at Urbana-Champaign.

\end{rSection}

%-------------------------------------------------------------------------------
%	CONTRIBUTED PRESENTATIONS
%-------------------------------------------------------------------------------

\begin{rSection}{Contributed Presentations}

%--Presentation-----------------------------------------------------------------
{\bf Muscarella ME}, O'Dwyer, JP (2017) A Phylogenetic Framework for Trait
 Innovation and Selection in Microbial Communities. Ecological Society of America Annual Meeting, Portland OR.

%--Presentation-----------------------------------------------------------------
Peralta AL, {\bf Muscarella ME} (2017) How can we manage microbial functions to restore ecosystem services in human-dominated landscapes? Ecological Society of America Annual Meeting, Portland OR.

%--Presentation-----------------------------------------------------------------
  {\bf Muscarella ME}, Lennon JT (2015) Bacterial growth efficiency: do
  consumer and resource diversity influence the fate of carbon in aquatic
  ecosystems? Ecological Society of America 100th Annual Meeting, Baltimore MD.

%--Presentation-----------------------------------------------------------------
  {\bf Muscarella ME}, Locey KJ, Nevo E, Raz S, Lennon JT (2014) Microbial
  community assembly at Evolution Canyon: Does dormancy dilute the effects of
  dispersal and filtering? Ecological Society of America 99th Annual Meeting,
  Sacramento CA.

%--Presentation-----------------------------------------------------------------
  {\bf Muscarella ME}, Bird KC, Larsen ML, Placella SA, Lennon JT (2014)
  Phosphorus resource heterogeneity affects the structure and function of
  microbial food webs. American Society of Limnology and Oceanography, Portland
  OR.

%--Presentation-----------------------------------------------------------------
  {\bf Muscarella ME}, Bird KC, Larsen ML, Placella SA, Lennon JT (2014)
  Phosphorus resource heterogeneity affects the structure and function of
  microbial food webs. Midwest Ecology and Evolution Conference, Dayton OH.

%--Presentation-----------------------------------------------------------------
  {\bf Muscarella ME}, Jones SE, Lennon JT (2013) Species Sorting Along a
  Subsidy Gradient Affects Community Stability. Ecological Society of America
  98th Annual Meeting, Minneapolis MN.

%--Presentation-----------------------------------------------------------------
  {\bf Muscarella ME}, Jones SE, Lennon JT (2013) Life in brown waters: Aquatic
  bacteria respond to increased terrestrial carbon loading. Midwest Ecology and
  Evolution Conference, South Bend, IN.

%--Presentation-----------------------------------------------------------------
  Lennon JT, {\bf Muscarella ME}, Jones SE (2013) Bacteria and browning:
  implications of terrestrial carbon subsidies for aquatic ecosystems. American
  Society of Limnology and Oceanography, New Orleans, LA.

%--Presentation-----------------------------------------------------------------
  {\bf Muscarella ME}, Jones SE, Lennon JT (2013) Life in brown waters: Aquatic
  bacterial responses to increased terrestrial carbon loading. American Society
  of Limnology and Oceanography, New Orleans, LA

%--Presentation-----------------------------------------------------------------
  {\bf Muscarella ME}, Jones SE, Lennon JT (2012) Life in brown waters: Aquatic
  bacteria respond to increased terrestrial carbon loading. LTER All Scientists
  Meeting, Estes Park, CO.

%--Presentation-----------------------------------------------------------------
  Booth MG, Gifford S, Doherty M, {\bf Muscarella M}, and Moran MA (2010)
  Expression of two carbon metabolism genes identified thorough transcriptomic
  analysis of estuarine bacterial communities of Sapelo Island, GA, U.S.A.
  International Society of Microbial Ecology Conference, Seattle, WA.

%--Presentation-----------------------------------------------------------------
  Doherty M, Poretsky R, {\bf Muscarella ME}, Moran MA, Booth MG (2009) Tracking
  Metabolism of an Important Terrestrial Carbon Source by Marine
  Bacterioplankton. Coastal and Estuarine Research Federation 20th Biennial
  Conference. Portland, OR.

%--Presentation-----------------------------------------------------------------
  {\bf Muscarella M}, Awong-Taylor J, Zettler J (2009) The Inability of
  Pathogenic and Nonpathogenic Strains of Escherichia coli to Survive in Coastal
  Beach Sand. 2009 Annual Conference of the Southeastern Branch American Society
  for Microbiology. Savannah, GA.

%--Presentation-----------------------------------------------------------------
  {\bf Muscarella M}, Awong-Taylor J (2008) Role of Curli Fibers in the Adhesion
  of Escherichia coli O157:H7 to Bean Sprouts. American Society for Microbiology
  108th Annual Meeting. Boston, MA.

%--Presentation-----------------------------------------------------------------
  {\bf Muscarella M}, Awong-Taylor J, Zettler J (2008) The Potential for
  Pathogenic and non-pathogenic Escherichia coli to Survive in Beach Sand from
  Tybee Island, GA. Association of Southeastern Biologists 69th Annual Meeting.
  Spartanburg, SC.

%--Presentation-----------------------------------------------------------------
  {\bf Muscarella M}, Awong-Taylor J (2008) A Method to Compare the
  Effectiveness of Different Washes on Removal Rates of E. coli from Plant
  Roots. Southern Regional Honors Council 36th Annual Conference. Birmingham,
  Al.

%--Presentation-----------------------------------------------------------------
  Griffiths L, Bass  C, {\bf Muscarella M}, Awong-Taylor J, Craven K (2006)
  Using Traditional and Molecular Techniques to Determine if Microbial
  Contamination Plays a Role in Embryonic Death of Loggerhead Sea Turtle Eggs.
  Florida Academy of Sciences 70th Annual Meeting. Melbourne, Fl

\end{rSection}


%-------------------------------------------------------------------------------
%	ACADEMIC ADVISORS
%-------------------------------------------------------------------------------

\begin{rSection}{Academic Advisors}
  {\bf James P. O'Dwyer} University of Illinois (Postdoc)

  {\bf Jay T. Lennon}, Indiana University (Ph.D.)

  {\bf Judy Awong-Taylor}, Armstrong State University (B.S.)

\end{rSection}

%-------------------------------------------------------------------------------
%	MENTEES
%-------------------------------------------------------------------------------

\begin{rSection}{Mentees}

  {\bf \em Undergraduate Students}: \\
    Belen Muniz ({\em University of Illinois} 2017)\\
    Mollie Carrison ({\em Indiana University} 2015 -- 2016)\\
    Rachel Ferrill ({\em Transylvania University} 2015) \\
    Xia Meng Howey ({\em Indiana University} 2012 -- 2014)

  {\bf \em High School Students}: \\
    Dakayla Calhoun ({\em Shortridge International Baccalaureate High
    School, Indianapolis, IN} 2015)\\
    Nick Nelson ({\em Bishop Noll Institute, Hammond, IN} 2012)

\end{rSection}


\end{document}
